---
title: "Supplementary documents"
date: " Last edited `r format(Sys.time(), '%B %d, %Y')`"
output:
  word_document: default
---

```{r setup, message=FALSE, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)

pacman::p_load(rio,
               here,
               gt,
               broom.mixed,
               flextable,
               tidyverse)

# Making a table of content
devtools::source_gist("c83e078bf8c81b035e32c3fc0cf04ee8",
                      filename = 'render_toc.R')
```

# Table of Contents

```{r toc, echo=FALSE} 
# render_toc("Supplementary documents.Rmd")
```

```{r load data}
load(here("0.data", "dpsir_clean_x0008_countriesfiltered241207.RData"))
```

# S1 Table - List of countries included in the study

```{r  s1-table}
summary_df <- import(here("0.data", "response_v2.csv")) %>% 
  select(c("EORA_a3", "Country", "Global.Region", "Continent")) %>% 
  distinct() %>% 
  mutate(Country = recode(Country, "The former Yugoslav Republic of Macedonia"=  "North Macedonia")) %>%
  dplyr::rename(ISO3 ="EORA_a3")


summary_df <- dpsir  %>%
  select(c("ISO3", "change", "RESPONSE", "income")) %>%
  na.omit() %>% 
  select(c("ISO3", "income")) %>% 
  distinct() %>%
  left_join(summary_df, by="ISO3") %>% 
  rename(Income = "income") %>% 
  select(c("ISO3", "Country", "Continent","Income"))
summary_df$Continent[summary_df$Continent == "Australia"] <- "Oceania"
summary_df$Continent[summary_df$Continent == "North America and Caribbean"] <- "North America"
summary_df$Continent[summary_df$Continent == "South and Central America"] <- "South America"

summary_df %>% 
  arrange(ISO3)  %>%  
  gt(groupname_col = "Continent") %>%
  tab_style(
    style = list(cell_text(weight = "bold")),
    locations = cells_row_groups()) %>%
  tab_footnote(
    footnote = "Number of Countries = 73")  %>%
  tab_footnote(
    footnote = "HIC refers for High Income Countries, LMIC refers for Low and Middle Income Countries")
```

\pagebreak

# S2 Table. Indicator selection for Driver categories.

\pagebreak

# S3 Table. Indicator selection for Use and Resistance categories.

\pagebreak

# S4 Table. Indicator selection for DRI (exposure) category.

\pagebreak

# S5 Table. Ecological variables used as covariates.

\pagebreak

# S6 Table. Governance Syndrome questions.

\pagebreak

# S7 Table - Action categories and subcategories

```{r}
response_categories <- data.frame(
  `Action sub categories` = c(
    "AMR Training (Human Health)",
    "AMR Training (Animal Health and Food Prod)",
    "AMR Awareness (Human Health)",
    "AMR Awareness (Animal Health and Food Prod)",
    "Monitoring System for AMU (Animals and Crop)",
    "AMR Surveillance System (Humans)",
    "Monitoring System for AMU (Human Health)",
    "AMR Surveillance System (Animals and Foods)",
    "Veterinary Services",
    "One Health Arrangements",
    "NAP progress",
    "AMS and Regulation (Human)",
    "AMS and Regulation (Ani&Crop)",
    "Contamination Prevention",
    "IPC",
    "AMU Prevention"
  ),
  Category = c(
    "Awareness and Education",
    "Awareness and Education",
    "Awareness and Education",
    "Awareness and Education",
    "Monitoring and Surveillance",
    "Monitoring and Surveillance",
    "Monitoring and Surveillance",
    "Monitoring and Surveillance",
    "General",
    "General",
    "General",
    "Regulation",
    "Regulation",
    "Regulation",
    "Prevention",
    "Prevention"
  )
)

response_categories %>% 
  rename("Action sub-categories" = `Action.sub.categories`) %>% 
  gt(groupname_col = "Category") %>%
  tab_style(
    style = list(cell_text(weight = "bold")),
    locations = cells_row_groups()) %>%
  tab_header("The overall governmental action score (action) is calculated as the average of subcategories (Awareness and Education, Monitoring and Surveillance, General, Regulation, Prevention).") %>% 
  tab_footnote(
    footnote = "Subcategories are not included in Animal Data Analysis and Figure 4",
    locations = cells_body(columns = `Action sub-categories`, rows = c(9, 10, 11, 15, 16))
  ) %>% 
  opt_footnote_marks(marks = "standard")


```

\pagebreak

# S8 Table. Model Formulas for Association between Action and Indicator Linear Trend and Categorical Trend
\pagebreak

#S12-S24 Tables
\pagebreak

```{r child-document4, child='2.2s.ActionCategories.Rmd', echo=FALSE}

```


