---
title: "Statistics"
output:
  html_document:
    df_print: paged
---

```{r all setup the packages, message=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE)

# install.packages("pacman")
# after installing pacman, basically you don't need to install any other packages
pacman::p_load(
 rio,
 dplyr,
 readr,
 tidyr,
 lme4,
 MuMIn,
 data.table,
 here,
 stringr,
 gtsummary,    # summary statistics and tests
 rstatix,      # summary statistics and statistical tests
 janitor,      # adding totals and percents to tables
 reshape2,
 tidyverse)     # data management + ggplot2 graphics   


rm(list = ls())
load(here("0.data", "dpsir_clean_x0008_countriesfiltered241207.RData"))
dpsir <- dpsir %>% left_join(driver_comp_x0008 %>% select(-c("DPSIR")), by= "ISO3")
# make sure na.omit is on - default version
options(na.action = "na.omit")
dpsir_final <- dpsir_final %>% filter(income== "LMIC")
dpsir <- dpsir %>% filter(income== "LMIC")
```


# GLOBMODs
globmods are named after the rownames from the excel file. "models sheet DPSIR 211123_EP.xlsb"

### 2- globmod.rDPSIRir2

```{r LMIC dframe.gc}
# # # dframe.gc-----------------------
dframe.gc.con <- dpsir %>%
  select(ISO3, DPSIR) %>% 
  pivot_wider(names_from = DPSIR, values_from = DPSIR) %>% 
  filter(!is.na(USE) | !is.na(RESISTANCE) | !is.na(DRI))

# select those countries from the conditioned dataframe
dframe.gc <- dpsir[dpsir$ISO3 %in% dframe.gc.con$ISO3, ] %>% 
  select(c("ISO3", "income","SHORTNAME", "DPSIR","x0008","change", "infTotal", "sanTotal", "vacTotal", "workTotal", "gini","PopDensity","prod.per.area","meantmpAreaPop","GDPcap_mean", "AwarenessandEducation", "General", "MonitoringandSurveillance", "RESPONSE")) %>%
  na.omit()

# if I don't include drop_na sample size is 250 and model has 156 observations. When I include drop_na(sample size is 156. Model results are same in both case.
# # globmod.rDPSIRir2-----------------------------------------------------------
globmod.rDPSIRir2 <- lmer(formula= change ~ 
                            RESPONSE*DPSIR + 
                            General*DPSIR + 
                            MonitoringandSurveillance*DPSIR + 
                            AwarenessandEducation*DPSIR + 
                            sanTotal*DPSIR + 
                            infTotal*DPSIR + 
                            workTotal*DPSIR + 
                            vacTotal*DPSIR + 
                            GDPcap_mean*DPSIR + 
                            PopDensity*DPSIR + 
                            gini*DPSIR + 
                            prod.per.area*DPSIR + 
                            meantmpAreaPop*DPSIR + 
                            x0008*DPSIR + 
                            (1|ISO3), 
                          data = dframe.gc) 
globmod.rDPSIRir2_sum <- summary(globmod.rDPSIRir2)
```

### 3- globmod.rDPSIRir2.noDr

```{r LMIC globmod.rDPSIRir2.noDr}
###dframe.gc.noDr
#exclude the explanatory variables
dframe.gc.noDr <- dpsir[dpsir$ISO3 %in% dframe.gc.con$ISO3, ] %>%
  select(c("ISO3", "income","SHORTNAME", "DPSIR","x0008","change", "gini","PopDensity","prod.per.area","meantmpAreaPop","GDPcap_mean", "AwarenessandEducation", "General", "MonitoringandSurveillance", "RESPONSE")) %>% 
  na.omit()


globmod.rDPSIRir2.noDr <- lmer(formula= change ~ 
                                 RESPONSE*DPSIR + 
                                 General*DPSIR + 
                                 MonitoringandSurveillance*DPSIR + 
                                 AwarenessandEducation*DPSIR + 
                                 GDPcap_mean*DPSIR +  
                                 PopDensity*DPSIR + 
                                 gini*DPSIR + 
                                 prod.per.area*DPSIR + 
                                 meantmpAreaPop*DPSIR + 
                                 x0008*DPSIR +
                                 (1|ISO3), 
                               data = dframe.gc.noDr) 
globmod.rDPSIRir2.noDr_sum <- summary(globmod.rDPSIRir2.noDr)

```



### 4- globmod.dframe.gc.aP.noDr

```{r LMIC  globmod.dframe.gc.aP.noDr}
###dframe.gc.aP.noDr 
dframe.gc.aP.noDr.con <- dpsir %>%
  select(ISO3, DPSIR) %>% 
  pivot_wider(names_from = DPSIR, values_from = DPSIR) %>% 
  filter(!is.na(USE))
dframe.gc.aP.noDr <- dpsir[dpsir$ISO3 %in% dframe.gc.aP.noDr.con$ISO3, ]  %>% select(-c("sanTotal","infTotal","vacTotal", "workTotal")) %>% na.omit()

globmod.dframe.gc.aP.noDr <- lmer(formula = change ~ 
    RESPONSE * DPSIR + 
    General * DPSIR + 
    MonitoringandSurveillance * DPSIR + 
    AwarenessandEducation * DPSIR + 
    GDPcap_mean * DPSIR + 
    PopDensity * DPSIR + 
    gini * DPSIR + 
    prod.per.area * DPSIR + 
    meantmpAreaPop * DPSIR + 
    x0008 * DPSIR + 
    (1 | ISO3), 
    data = dframe.gc.aP.noDr)
globmod.dframe.gc.aP.noDr_sum <- summary(globmod.dframe.gc.aP.noDr) 
```

### 5- globmod.dframe.gc.aS.noDr

```{r LMIC globmod.dframe.gc.aS.noDr}
###dframe.gc.aS.noDr
dframe.gc.aS.noDr.con <- dpsir %>%
  select(ISO3, DPSIR) %>% 
  pivot_wider(names_from = DPSIR, values_from = DPSIR) %>% 
  filter(!is.na(RESISTANCE))
dframe.gc.aS.noDr <- dpsir[dpsir$ISO3 %in% dframe.gc.aS.noDr.con$ISO3, ] %>% select(-c("sanTotal","infTotal","vacTotal", "workTotal")) %>% na.omit()

globmod.dframe.gc.aS.noDr <- lmer(formula = change ~ 
    RESPONSE * DPSIR + 
    General * DPSIR + 
    MonitoringandSurveillance * DPSIR + 
    AwarenessandEducation * DPSIR + 
    GDPcap_mean * DPSIR + 
    PopDensity * DPSIR + 
    gini * DPSIR + 
    prod.per.area * DPSIR + 
    meantmpAreaPop * DPSIR + 
    x0008 * DPSIR + 
    (1 | ISO3), 
    data = dframe.gc.aS.noDr)
globmod.dframe.gc.aS.noDr_sum <- summary(globmod.dframe.gc.aS.noDr) 
```

### 6- globmod.dframe.gc.aI.noDr

```{r LMIC dframe.gc.aI.noDr}
###dframe.gc.aI.noDr
dframe.gc.aI.noDr.con <- dpsir %>%
  select(ISO3, DPSIR) %>% 
  pivot_wider(names_from = DPSIR, values_from = DPSIR) %>% 
  filter(!is.na(DRI))
dframe.gc.aI.noDr <- dpsir[dpsir$ISO3 %in% dframe.gc.aI.noDr.con$ISO3, ] %>% select(-c("sanTotal","infTotal","vacTotal", "workTotal")) %>% na.omit()

globmod.dframe.gc.aI.noDr <- lmer(formula= change  ~ 
                                    RESPONSE * DPSIR + 
                                    General * DPSIR + 
                                    MonitoringandSurveillance * DPSIR + 
                                    AwarenessandEducation * DPSIR + 
                                    GDPcap_mean * DPSIR + 
                                    PopDensity * DPSIR + 
                                    gini * DPSIR + 
                                    prod.per.area * DPSIR + 
                                    meantmpAreaPop * DPSIR + 
                                    x0008 * DPSIR + 
                                    (1 | ISO3), 
                                  data = dframe.gc.aI.noDr)

globmod.dframe.gc.aI.noDr_sum <- summary(globmod.dframe.gc.aI.noDr) 
```

### 7- globmod.dframe.gc.aP

```{r LMIC dframe.gc.aP}
###dframe.gc.aP
dframe.gc.aP.con <- dpsir %>%
  select(ISO3, DPSIR) %>% 
  pivot_wider(names_from = DPSIR, values_from = DPSIR) %>% 
  filter(!is.na(USE))
dframe.gc.aP <- dpsir[dpsir$ISO3 %in% dframe.gc.aP.con$ISO3, ] %>% na.omit()

globmod.dframe.gc.aP <- lmer(formula = change ~ 
    RESPONSE * DPSIR + 
    General * DPSIR + 
    MonitoringandSurveillance * DPSIR + 
    AwarenessandEducation * DPSIR + 
    sanTotal * DPSIR + 
    infTotal * DPSIR + 
    workTotal * DPSIR + 
    vacTotal * DPSIR + 
    GDPcap_mean * DPSIR + 
    PopDensity * DPSIR + 
    gini * DPSIR + 
    prod.per.area * DPSIR + 
    meantmpAreaPop * DPSIR + 
    x0008 * DPSIR + 
    (1 | ISO3), 
    data = dframe.gc.aP)
globmod.dframe.gc.aP_sum <- summary(globmod.dframe.gc.aP) 

```

### 8- globmod.dframe.gc.aS

```{r LMIC dframe.gc.aS}
###dframe.gc.aS
dframe.gc.aS.con <- dpsir %>%
  select(ISO3, DPSIR) %>% 
  pivot_wider(names_from = DPSIR, values_from = DPSIR) %>% 
  filter(!is.na(RESISTANCE))
dframe.gc.aS <- dpsir[dpsir$ISO3 %in% dframe.gc.aS.con$ISO3, ] %>% na.omit()

globmod.dframe.gc.aS <- lm(formula= change  ~  
                               RESPONSE*DPSIR +
                               General*DPSIR + 
                               MonitoringandSurveillance*DPSIR + 
                               AwarenessandEducation*DPSIR  + 
                               sanTotal*DPSIR + 
                               infTotal*DPSIR + 
                               workTotal*DPSIR  + 
                               vacTotal*DPSIR  + 
                               GDPcap_mean*DPSIR +  
                               PopDensity*DPSIR + 
                               gini*DPSIR + 
                               prod.per.area*DPSIR + 
                               meantmpAreaPop*DPSIR + 
                               x0008*DPSIR 
                               , data = dframe.gc.aS)
globmod.dframe.gc.aS_sum <- summary(globmod.dframe.gc.aS) 

```

### 9- globmod.dframe.gc.aI

```{r LMIC dframe.gc.aI}
###dframe.gc.aI
dframe.gc.aI.con <- dpsir %>%
  select(ISO3, DPSIR) %>% 
  pivot_wider(names_from = DPSIR, values_from = DPSIR) %>% 
  filter(!is.na(DRI))
dframe.gc.aI <- dpsir[dpsir$ISO3 %in% dframe.gc.aI.con$ISO3, ] %>% na.omit()

globmod.dframe.gc.aI <- lm(formula= change  ~  
                               RESPONSE*DPSIR +
                               General*DPSIR + 
                               MonitoringandSurveillance*DPSIR + 
                               AwarenessandEducation*DPSIR  + 
                               sanTotal*DPSIR + 
                               infTotal*DPSIR + 
                               workTotal*DPSIR  + 
                               vacTotal*DPSIR  + 
                               GDPcap_mean*DPSIR +  
                               PopDensity*DPSIR + 
                               gini*DPSIR + 
                               prod.per.area*DPSIR + 
                               meantmpAreaPop*DPSIR + 
                               x0008*DPSIR 
                               , data = dframe.gc.aI)
globmod.dframe.gc.aI_sum <-summary(globmod.dframe.gc.aI)

```

### *10- globmod.dframe.iD

```{r LMIC dframe.iD}
# dframe.iD
 driver_lvl2 <- dpsir_final %>% 
  filter(level== "level 2" & DPSIR == "DRIVERS") %>% select(c("ISO3", "income", "SHORTNAME", "DPSIR", "change", "x0008" )) %>% 
  unique() %>% 
  left_join(eco_vars, by = c("ISO3"))

driver_lvl2_df_mod <- driver_lvl2 %>% left_join(survey_vars, by="ISO3") 

dframe.iD.con <- dpsir_final %>%
  select(ISO3, DPSIR) %>% unique() %>% 
  pivot_wider(names_from = DPSIR, values_from = DPSIR) %>% 
  filter(!is.na(USE) | !is.na(RESISTANCE) | !is.na(DRI))
# select those countries from the conditioned dataframe
dframe.iD <- driver_lvl2_df_mod[driver_lvl2_df_mod$ISO3 %in% dframe.iD.con$ISO3, ] %>% na.omit()
dframe.iD$ISO3 <- as.factor(dframe.iD$ISO3)
dframe.iD$DPSIR <- as.factor(dframe.iD$DPSIR)
### THIS MODEL IS EXCLUDED BECAUSE THE DF HAS ONLY ! TYPE OF DPSIR CATEGORY HENCE CANT BE INCLUDED AS AN INTERACTION EFFECT
### globmod.dframe.iD
globmod.dframe.iD <- lmer(formula= change  ~
                            RESPONSE +
                            General +
                            MonitoringandSurveillance+
                            AwarenessandEducation+
                            GDPcap_mean+
                            PopDensity+
                            gini+
                            prod.per.area+
                            meantmpAreaPop+
                            x0008+
                            (1|ISO3) +
                            (1|SHORTNAME),
                            data = dframe.iD)

globmod.dframe.iD_sum <- summary(globmod.dframe.iD)
```

### *11- globmod.dframe.iP

```{r LMIC  globmod.dframe.iP}
# dframe.iP
 use_lvl2 <- dpsir_final %>% 
  filter(level== "level 2" & DPSIR == "USE") %>% select(c("ISO3", "income", "change", "x0008","SHORTNAME", "DPSIR")) %>% 
  unique()
use_lvl2_eco_vars <- use_lvl2 %>% left_join(eco_vars, by = c("ISO3")) %>% select(-c("DPSIR"))

use_lvl2_df_mod <- use_lvl2_eco_vars %>% left_join(survey_vars, by ="ISO3") %>% left_join(driver_comp_x0008 %>% select(-c("DPSIR")), by="ISO3")
use_lvl2_df_mod$ISO3 <- as.factor(use_lvl2_df_mod$ISO3)
##dframe.iP and use_lvl2_df_mod are identical
dframe.iP <- use_lvl2_df_mod %>% na.omit()

globmod.dframe.iP <-  lmer(formula= change  ~
                            RESPONSE+
                            General+
                            MonitoringandSurveillance+
                            AwarenessandEducation+
                            sanTotal + 
                            infTotal +
                            workTotal +
                            vacTotal + 
                            GDPcap_mean+
                            PopDensity+
                            gini+
                            prod.per.area+
                            meantmpAreaPop+
                            x0008+
                            (1|ISO3) + 
                            (1|SHORTNAME),
                           data = dframe.iP)

globmod.dframe.iP_sum <- summary(globmod.dframe.iP)

```

### *12- globmod.dframe.iS

```{r LMIC globmod.dframe.iS}
# dframe.iS
 resistance_lvl2 <- dpsir_final %>% 
  filter(level== "level 2" & DPSIR == "RESISTANCE") %>% select(c("ISO3", "income","change", "SHORTNAME", "DPSIR" , "x0008")) %>% 
  unique() 
resistance_lvl2_df <- resistance_lvl2 %>% left_join(eco_vars, by = c("ISO3")) %>% select(-c("DPSIR"))

resistance_lvl2_df_mod <- resistance_lvl2_df %>%left_join(survey_vars, by ="ISO3") %>% left_join(driver_comp_x0008 %>% select(-c("DPSIR")), by="ISO3")

resistance_lvl2_df_mod$ISO3 <- as.factor(resistance_lvl2_df_mod$ISO3)
resistance_lvl2_df_mod$SHORTNAME <- as.factor(resistance_lvl2_df_mod$SHORTNAME)

##dframe.iS and resistance_lvl2_df_mod are identical
dframe.iS <- resistance_lvl2_df_mod %>% drop_na()

globmod.dframe.iS <- lmer(formula= change  ~
                            RESPONSE+
                            General+
                            MonitoringandSurveillance+
                            AwarenessandEducation+
                            sanTotal + 
                            infTotal +
                            workTotal +
                            vacTotal + 
                            GDPcap_mean+
                            PopDensity+
                            gini+
                            prod.per.area+
                            meantmpAreaPop+
                            x0008+
                            (1|ISO3) + 
                            (1|SHORTNAME),
                            data = dframe.iS)

globmod.dframe.iS_sum <- summary(globmod.dframe.iS)

```

### * 13- globmod.dframe.gcI-NA

```{r}
# dframe.gcI
DRI <- dpsir_final %>% 
  filter(DPSIR == "DRI") %>% 
  select(c("ISO3", "income", "SHORTNAME", "DPSIR", "x0008", "change")) %>% 
  unique()

DRI_df <- DRI %>% 
  left_join(eco_vars, by = c("ISO3"))
#%>%   select(-c("DPSIR"))

DRI_df_mod <- DRI_df %>% 
  left_join(survey_vars, by ="ISO3") %>% left_join(driver_comp_x0008 %>% select(-c("DPSIR")), by="ISO3")

DRI_df_mod$ISO3 <- as.factor(DRI_df_mod$ISO3)

##dframe.gcI and DRI_df_mod are identical
dframe.gcI <- DRI_df_mod %>% drop_na() #%>% select(-c("SHORTNAME"))
dframe.gcI$ISO3 <- as.factor(dframe.gcI$ISO3)

globmod.dframe.gcI <- lm(formula=change ~
                             RESPONSE+
                             General+
                             MonitoringandSurveillance+
                             AwarenessandEducation+
                             infTotal+
                             sanTotal+
                             vacTotal+
                             workTotal+
                             GDPcap_mean+
                             PopDensity+
                             gini+
                             prod.per.area+
                             meantmpAreaPop+
                             x0008,
                              data = dframe.gcI)
globmod.dframe.gcI_sum <- summary(globmod.dframe.gcI)
```

### 14- globmod.dframe.gcDPS

```{r}
###dframe.gcDPS
dframe.gcDPS.con <- dpsir %>%
  select(ISO3, DPSIR) %>% 
  pivot_wider(names_from = DPSIR, values_from = DPSIR) %>% 
  filter(!is.na(USE) | !is.na(RESISTANCE))
# select those countries from the conditioned dataframe
dframe.gcDPS <- dpsir[dpsir$ISO3 %in% dframe.gcDPS.con$ISO3, ] %>%  
  filter(! DPSIR == "DRI") %>% drop_na()

globmod.dframe.gcDPS <- lmer(formula= change  ~  
                               RESPONSE*DPSIR + 
                               General*DPSIR + 
                               MonitoringandSurveillance*DPSIR + 
                               AwarenessandEducation*DPSIR + 
                               sanTotal*DPSIR + 
                               infTotal*DPSIR + 
                               workTotal*DPSIR + 
                               vacTotal*DPSIR + 
                               GDPcap_mean*DPSIR +
                               PopDensity*DPSIR + 
                               gini*DPSIR + 
                               prod.per.area*DPSIR + 
                               meantmpAreaPop*DPSIR + 
                               x0008*DPSIR +
                               (1|ISO3), data = dframe.gcDPS)
globmod.dframe.gcDPS_sum <- summary(globmod.dframe.gcDPS) 
```

### 15- globmod.dframe.gcPSI

```{r}
###dframe.gcPSI
dframe.gcPSI.con <- dpsir %>%
  select(ISO3, DPSIR) %>% 
  pivot_wider(names_from = DPSIR, values_from = DPSIR) %>% 
  filter(!is.na(USE) | !is.na(RESISTANCE) | !is.na(DRI))
# select those countries from the conditioned dataframe
dframe.gcPSI <- dpsir[dpsir$ISO3 %in% dframe.gcPSI.con$ISO3, ] %>%  filter(! DPSIR == "DRIVERS") %>% drop_na()
options(na.action = "na.omit")

globmod.dframe.gcPSI <- lmer(formula= change  ~  
                               RESPONSE*DPSIR + 
                               General*DPSIR + 
                               MonitoringandSurveillance*DPSIR + 
                               AwarenessandEducation*DPSIR + 
                               sanTotal*DPSIR + 
                               infTotal*DPSIR + 
                               workTotal*DPSIR + 
                               vacTotal*DPSIR + 
                               GDPcap_mean*DPSIR +
                               PopDensity*DPSIR + 
                               gini*DPSIR + 
                               prod.per.area*DPSIR + 
                               meantmpAreaPop*DPSIR + 
                               x0008*DPSIR +
                               (1|ISO3),
                               data = dframe.gcPSI)
globmod.dframe.gcPSI_sum <- summary(globmod.dframe.gcPSI) 
```

### 16- globmod.dframe.gcDP

```{r}
###dframe.gcDP
dframe.gcDP.con <-  dpsir %>%
  select(ISO3, DPSIR) %>% 
  pivot_wider(names_from = DPSIR, values_from = DPSIR) %>% 
  filter(!is.na(USE))
# select those countries from the conditioned dataframe
dframe.gcDP <- dpsir[dpsir$ISO3 %in% dframe.gcDP.con$ISO3, ] %>%  filter(DPSIR == "DRIVERS" | DPSIR == "USE") %>% drop_na()

globmod.dframe.gcDP <- lmer(formula= change  ~  
                               RESPONSE*DPSIR + 
                               General*DPSIR + 
                               MonitoringandSurveillance*DPSIR + 
                               AwarenessandEducation*DPSIR + 
                               sanTotal*DPSIR + 
                               infTotal*DPSIR + 
                               workTotal*DPSIR + 
                               vacTotal*DPSIR + 
                               GDPcap_mean*DPSIR +
                               PopDensity*DPSIR + 
                               gini*DPSIR + 
                               prod.per.area*DPSIR + 
                               meantmpAreaPop*DPSIR + 
                               x0008*DPSIR +
                               (1|ISO3), data = dframe.gcDP)
globmod.dframe.gcDP_sum <- summary(globmod.dframe.gcDP) 

```

### 17- globmod.dframe.gcPS

```{r}
###dframe.gcPS
dframe.gcPS.con <-  dpsir %>%
  select(ISO3, DPSIR) %>% 
  pivot_wider(names_from = DPSIR, values_from = DPSIR) %>% 
  filter(!is.na(USE)| !is.na(RESISTANCE))
# select those countries from the conditioned dataframe
dframe.gcPS <- dpsir[dpsir$ISO3 %in% dframe.gcPS.con$ISO3, ] %>%  filter(DPSIR == "USE" | DPSIR == "RESISTANCE") %>% drop_na()

globmod.dframe.gcPS <- lmer(formula= change  ~  
                               RESPONSE*DPSIR + 
                               General*DPSIR + 
                               MonitoringandSurveillance*DPSIR + 
                               AwarenessandEducation*DPSIR + 
                               sanTotal*DPSIR + 
                               infTotal*DPSIR + 
                               workTotal*DPSIR + 
                               vacTotal*DPSIR + 
                               GDPcap_mean*DPSIR +
                               PopDensity*DPSIR + 
                               gini*DPSIR + 
                               prod.per.area*DPSIR + 
                               meantmpAreaPop*DPSIR + 
                               x0008*DPSIR +
                               (1|ISO3),data = dframe.gcPS)
globmod.dframe.gcPS_sum <- summary(globmod.dframe.gcPS) 

```

### 18- globmod.dframe.gcSI -NA

```{r}
###dframe.gcSI
dframe.gcSI.con <- dpsir %>%
  select(ISO3, DPSIR) %>% 
  pivot_wider(names_from = DPSIR, values_from = DPSIR) %>% 
  filter(!is.na(RESISTANCE) | !is.na(DRI))
# select those countries from the conditioned dataframe
dframe.gcSI <- dpsir[dpsir$ISO3 %in% dframe.gcSI.con$ISO3, ] %>%  filter(DPSIR == "RESISTANCE" | DPSIR == "DRI") %>% drop_na()

globmod.dframe.gcSI <- lm(formula= change  ~  
                               RESPONSE*DPSIR + 
                               General*DPSIR + 
                               MonitoringandSurveillance*DPSIR + 
                               AwarenessandEducation*DPSIR + 
                               sanTotal*DPSIR + 
                               infTotal*DPSIR + 
                               workTotal*DPSIR + 
                               vacTotal*DPSIR + 
                               GDPcap_mean*DPSIR +
                               PopDensity*DPSIR + 
                               gini*DPSIR + 
                               prod.per.area*DPSIR + 
                               meantmpAreaPop*DPSIR + 
                               x0008*DPSIR 
                               , data = dframe.gcSI)

globmod.dframe.gcSI_sum <- summary(globmod.dframe.gcSI) 

```

#### LIST 

```{r}

# First clear all the unneccessary data. 
## Clear the condition dataframes
rm(list = ls()[grepl("\\.con$", ls())])
rm(list = ls()[grepl("\\_lvl2", ls())])
rm(DRI, DRI_df, DRI_df_mod)

#ls(pattern = "^dframe\\.")
#Make a large list from all existing dataframes
LMIC_df_list <- mget(c(
  "dframe.gc",
  "dframe.gc.noDr",
  "dframe.gc.aP.noDr",
  "dframe.gc.aS.noDr",
  "dframe.gc.aI.noDr",
  "dframe.gc.aP",
  "dframe.gc.aS",
  "dframe.gc.aI",
  "dframe.iD",
  "dframe.iP",
  "dframe.iS",
  "dframe.gcI",
  "dframe.gcDPS",
  "dframe.gcPSI",
  "dframe.gcDP",
  "dframe.gcPS",
  "dframe.gcSI"
))

#save globmod list
LMIC_globmod_list <- list(globmod.rDPSIRir2,
                     globmod.rDPSIRir2.noDr,               
                     globmod.dframe.gc.aP.noDr,
                     globmod.dframe.gc.aS.noDr,
                     globmod.dframe.gc.aI.noDr,
                     globmod.dframe.gc.aP,
                     globmod.dframe.gc.aS,
                     globmod.dframe.gc.aI,
                     globmod.dframe.iD,           
                     globmod.dframe.iP,
                     globmod.dframe.iS,
#                     globmod.dframe.gcI,
                     globmod.dframe.gcDPS, 
                     globmod.dframe.gcPSI,
                     globmod.dframe.gcDP,
                     globmod.dframe.gcPS)
#                     globmod.dframe.gcSI)

save.image(file = here("3.Model_Selection/3.1.CHANGE/3.1.3.LMIC_CHANGE", "LMIC_Define_Models_input.RData"))
```
